Ms 1

### 2017-09-25 ms1/ms1_display.Rmd
ms1 dx

pde_approp_table %>%
  filter(tier <= 2) %>%
  select(antibiotic, year, f) %>%
  group_by(antibiotic, year) %>%
  summarize(f=sum(f)) %>%
  ungroup() %>%
  spread(year, f) %>%
  left_join(pde_approp_trends, by='antibiotic') %>%
  mutate(raw_pct_change=(`2014`-`2011`)/`2011`,
         adj_pct_change=risk_ratio_f(or, `2011`) - 1) %>%
  mutate_at(vars(`2011`, `2014`, raw_pct_change, adj_pct_change),
            function(x) round(x*100, 2)) %>%
  select(antibiotic, `2011`, `2014`, raw_pct_change, adj_pct_change, adj.p) %>%
  arrange(desc(`2011`)) %>%
  kable
```

>>>>

pde_approp_table %>%
  filter(tier <= 2) %>%
  select(antibiotic, year, f) %>%
  group_by(antibiotic, year) %>%
  summarize(f=sum(f)) %>%
  ungroup() %>%
  spread(year, f) %>%
  left_join(pde_approp_trends, by='antibiotic') %>%
  mutate(raw_pct_change=(`2014`-`2011`)/`2011`,
         adj_pct_change=risk_ratio_f(or, `2011`) - 1) %>%
  mutate_at(vars(`2011`, `2014`, raw_pct_change, adj_pct_change),
            function(x) round(x*100, 2)) %>%
  select(antibiotic, `2011`, `2014`, raw_pct_change, adj_pct_change, adj.p) %>%
  arrange(raw_pct_change) %>%
  kable
```
